---
title: "Portfoliomanagement and Financial Analysis - Assignment 2"
subtitle: "Submit until Monday 2020-09-28, 13:00"
author: "Winder, Anna-Sophie"
output: html_notebook
---



pacman::p_load(tidyverse,tidyquant,FFdownload,tsibble)


**Please** remember to put your assignment solutions in `rmd` format using **many** chunks and putting readable text in between, similar to my examples given in Research Methods and Assignment 1! Also, each student has to select his own set of 10 stocks having data available as of `2000-01-01`. Select by Sharpe-ratio, dominance or any other method (e.g. matching your first name).

## Exercise 1: Performance Analysis of Portfolios

Create (using four of the ten stocks) multiple portfolios using `tq_portfolio()`:

*  an equally weighted one, 
*  a market-value weighted one, and 
*  one where you create a trading strategy according to [https://www.datacamp.com/community/tutorials/r-trading-tutorial](https://www.datacamp.com/community/tutorials/r-trading-tutorial) - use the tools in the tidyquant package!! Trade your four stocks in a way that Portfolios weights (in sum) do never exceed +-1.

DO a performance analysis a la `vignette("TQ05-performance-analysis-with-tidyquant")`.

## Solution Exercise 1


getting 10 stocks from sp500 index
```{r}
AAPL <- tq_get("AAPL", get = "stock.prices", from =  "2000-01-01", to = "2020-09-01")
AMZN <- tq_get("AMZN", get = "stock-prices", from = "2000-01-01", to = "2020-09-01")
MSFT <- tq_get("MSFT", get = "stock.prices", from = "2000-01-01", to = "2020-09-01")
GOOG <- tq_get("MSFT", get = "stock.prices", from = "2000-01-01", to = "2020-09-01")
CSCO <- tq_get("CSCO", get = "stock.prices", from =  "2000-01-01", to = "2020-09-01")
QCOM <- tq_get("QCOM", get = "stock.prices", from =  "2000-01-01", to = "2020-09-01")
ADBE <- tq_get("ADBE", get = "stock.prices", from =  "2000-01-01", to = "2020-09-01")
NVDA <- tq_get("NVDA", get = "stock.prices", from =  "2000-01-01", to = "2020-09-01")
AMGN <- tq_get("AMGN", get = "stock.prices", from =  "2000-01-01", to = "2020-09-01")
GILD <- tq_get("GILD", get = "stock.prices", from =  "2000-01-01", to = "2020-09-01")
```
select four stocks - I selected CSCO, QCOM, NVDA and GILD
```{r getting returns from the four stocks}
monthly_returns_stocks <- c("CSCO", "QCOM", "NVDA", "GILD") %>%
  tq_get(get = "stock.prices", from = "2000-01-01", to = "2020-09-01") %>%
  group_by(symbol)%>%
  tq_transmute(adjusted, periodReturn, period = "monthly", col_rename =  "Ra")
monthly_returns_stocks
```

```{r create basline returns}
#to compare it with an index
monthly_returns_baseline <- "^GSPC" %>%
  tq_get(get = "stock.prices", from = "2000-01-01", to = "2020-09-01") %>%
  tq_transmute(adjusted, periodReturn, period = "monthly", col_rename = "Rb")
monthly_returns_baseline
```

```{r Aggregate portfolios}
#because we want 3 portfolios - we grow our portfolios, scalling a single portfolio to many
mult_monthly_returns_stocks <- monthly_returns_stocks %>%
  tq_repeat_df(n = 3)

mult_monthly_returns_stocks
```

* equally weighted one

first portfolio is equally weight =>
that is why we choose 25% for each
```{r}
stock_returns_monthly <- c("CSCO", "QCOM", "NVDA","GILD") %>%
    tq_get(get  = "stock.prices",
           from = "2000-01-01",
           to   = "2020-09-01") %>%
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Ra")
```
Second, get baseline asset returns, which is the exact same as Steps 1B and 2B from the Single Portfolio example.
```{r}
baseline_returns_monthly <- "XLK" %>%
    tq_get(get  = "stock.prices",
           from = "2016-01-01",
           to   = "2019-12-31") %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Rb")

stock_returns_monthly_multi <- stock_returns_monthly %>%
    tq_repeat_df(n = 3)
stock_returns_monthly_multi
```

Here’s what the weights table should look like for our example:
```{r}
weights <- c(0.25, 0.25, 0.25, 0.25,
             0.25, 0.25, 0.25, 0.25,
             0.25, 0.25, 0.25, 0.25)

stocks <- c("CSCO", "QCOM", "NVDA","GILD")
weights_table <-  tibble(stocks) %>%
    tq_repeat_df(n = 3) %>%
    bind_cols(tibble(weights)) %>%
    group_by(portfolio)
weights_table

portfolio_returns_monthly_multi <- stock_returns_monthly_multi %>%
    tq_portfolio(assets_col  = symbol, 
                 returns_col = Ra, 
                 weights     = weights_table, 
                 col_rename  = "Ra")
portfolio_returns_monthly_multi
```

Now just pass the the expanded stock_returns_monthly_multi and the weights_table to tq_portfolio for portfolio aggregation.
```{r}
portfolio_returns_monthly_multi <- mult_monthly_returns_stocks %>%
    tq_portfolio(assets_col  = symbol, 
                 returns_col = Ra, 
                 weights     = weights_table, 
                 col_rename  = "Ra")
portfolio_returns_monthly_multi
```
* a market-value weighted one
```{r a market-value weighted one}
library(rvest)
library(TTR)
library(dygraphs)
library(lubridate)

#https://finance.yahoo.com/quote/QCOM?p=QCOM&.tsrc=fin-srch&guccounter=1
#marketcaps: CSCO=212.095B;GILD=83.434B;NVDA=109.748B;QCOM=94.87B
marketcaps <- c(212.095, 83.434, 109.748, 94.87)
#compute the weights
weights <- marketcaps /sum(marketcaps)
#inspect summary statistics
summary(weights)
#show the weights
weights
```
```{r market value weighted portfolio}
#CSCO = 42,41%
#GILD = 16,68%
#NVDA= 21,94%
#QCOM = 18,97%


#*  one where you create a trading strategy according to [https://www.datacamp.com/community/tutorials/r-trading-tutorial](https://www.datacamp.com/community/tutorials/r-trading-tutorial) - use the tools in the tidyquant package!! Trade your four stocks in a way that Portfolios weights (in sum) do never exceed +-1.
```

```{r finding out about our own trading strategy}
library(rvest)
library(TTR)
library(lubridate)

#sma is used to produce moving averages of the stock prices --> same weight for all historical data
#we produce moving averages because we need them for our "trend following" trading strategy to compare it

sma_CSCO <- SMA(CSCO[, "close"], n=50)
sma_GILD <- SMA(GILD[, "close"], n=50)
sma_NVDA <- SMA(NVDA[, "close"], n=50)
sma_QCOM <- SMA(QCOM[, "close"], n=50)

sma_CSCO_200 <- SMA(CSCO[, "close"], n=200)
sma_GILD_200 <- SMA(GILD[, "close"], n=200)
sma_NVDA_200 <- SMA(NVDA[, "close"], n=200)
sma_QCOM_200 <- SMA(QCOM[, "close"], n=200)
```

alternatively you could have also used ema => it gives more weight to current data => maybe makes more sense

```{r creating dataframes for each stock with 200days and 50days moving averages}

library(tidyverse)
library(tidyquant)

#create a CSCO dataframe with the important data
CSCO_dates <- select(CSCO, date)
CSCO_dates

data.frame_CSCO <- data.frame(CSCO_dates, sma_CSCO_200, sma_CSCO)
data.frame_CSCO

#create a GILD dataframe with the important data
GILD_dates <- select(GILD, date)
GILD_dates

data.frame_GILD <- data.frame(GILD_dates, sma_GILD_200, sma_GILD)
data.frame_GILD

#create a QCOM dataframe with the important data
QCOM_dates <- select(QCOM, date)
QCOM_dates

data.frame_QCOM <- data.frame(QCOM_dates, sma_QCOM_200, sma_QCOM)
data.frame_QCOM

#creat a NVDA dataframe with the important data
NVDA_dates <- select(NVDA, date)
NVDA_dates

data.frame_NVDA <- data.frame(NVDA_dates, sma_NVDA_200, sma_NVDA)
data.frame_NVDA
``` 

```{r compare the second and the third colomn and fill them with 0 & 1}
# new column - fill with 0, but when 50day > 200 days, fill with 1

data.frame_CSCO['CSCO'] <- 0
data.frame_CSCO$CSCO[data.frame_CSCO$sma_CSCO > data.frame_CSCO$sma_CSCO_200] = 1  

data.frame_GILD['GILD'] <- 0
data.frame_GILD$GILD[data.frame_GILD$sma_GILD > data.frame_GILD$sma_GILD_200] = 1  

data.frame_QCOM['QCOM'] <- 0
data.frame_QCOM$QCOM[data.frame_QCOM$sma_QCOM > data.frame_QCOM$sma_QCOM_200] = 1  

data.frame_NVDA['NVDA'] <- 0
data.frame_NVDA$NVDA[data.frame_NVDA$sma_NVDA > data.frame_NVDA$sma_NVDA_200] = 1  
```

```{r sum up the colomn with 0 & 1}
#so we find out how many 1's are there --> on how many days we want to invest out of all
V_01 <- select(data.frame_CSCO, CSCO)
colSums(V_01, na.rm = TRUE)

nrow(data.frame_CSCO)
#calculate weight for CSCO
WEIGHT_CSCO <- colSums(V_01, na.rm = TRUE)/nrow(data.frame_CSCO)*100

V_02 <- select(data.frame_GILD, GILD)
colSums(V_02, na.rm = TRUE)

nrow(data.frame_GILD)
#calculate weight for GILD
WEIGHT_GILD <- colSums(V_02, na.rm = TRUE)/nrow(data.frame_GILD)*100

#calcuation for QCOM
V_03 <- select(data.frame_QCOM, QCOM)
colSums(V_03, na.rm = TRUE)

nrow(data.frame_QCOM)
#calculate weight QCOM
WEIGHT_QCOM <- colSums(V_03, na.rm = TRUE)/nrow(data.frame_QCOM)*100

#calculation for NVDA
V_04 <- select(data.frame_NVDA, NVDA)
colSums(V_04, na.rm = TRUE)

nrow(data.frame_NVDA)
#calculate weight NVDA
WEIGHT_NVDA <- colSums(V_04, na.rm = TRUE)/nrow(data.frame_NVDA)*100
``` 

```{r} 
#weight calculation 
all_weights <- sum(WEIGHT_CSCO, WEIGHT_GILD, WEIGHT_NVDA, WEIGHT_QCOM)

final_weight_CSCO <- WEIGHT_CSCO/all_weights
final_weight_GILD <- WEIGHT_GILD/all_weights
final_weight_NVDA <- WEIGHT_NVDA/all_weights
final_weight_QCOM <- WEIGHT_QCOM/all_weights


all_weights_tb <- tibble(final_weight_CSCO, final_weight_GILD, final_weight_QCOM, final_weight_NVDA)

rowSums(all_weights_tb)
```

```{r }
library(rvest)
library(TTR)
library(lubridate)
```

```{r create all the three portfolios}
#create new table of weights
weights_portfolio <- c(0.25, 0.25, 0.25, 0.25,
            weights[1], weights[2], weights[3], weights[4],
             final_weight_CSCO, final_weight_GILD, final_weight_QCOM, final_weight_NVDA)

stocks <- c("CSCO", "GILD", "NVDA", "QCOM")

weights_table <- tibble(stocks)%>%
    tq_repeat_df(n = 3) %>%
    bind_cols(tibble(weights_portfolio)) %>%
    group_by(portfolio)

weights_table
```

```{r we have to merge the expanded stock returns, the weights table for a portfolio aggregation}

portfolio_returns_monthly_multi <- mult_monthly_returns_stocks %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Ra,
               weights = weights_table,
               col_rename = "Ra")
portfolio_returns_monthly_multi
```

```{r Merge with the baseline using date as the key}
multiple_portfolio <- left_join(portfolio_returns_monthly_multi,
                                monthly_returns_baseline,
                                by = "date")
multiple_portfolio
```


```{r performance calculation}
multiple_portfolio %>%
  tq_performance(Ra = Ra, Rb = Rb, performance_fun = table.CAPM)
```

Beta measures a security's sensitivity to market risk (the lower the better)
Alpha - difference from expected and required return (the higher the better)


```{r}
#Sharpe Ratio
multiple_portfolio %>%
  tq_performance(Ra = Ra, Rb = Rb, performance_fun = SharpeRatio)
#the higher the Sharpe Ratio the better
```


## Exercise 2: The mu/sigma diagram

For the 10 stocks in your sample, calculate mu and sigma for the entire and 3 subperiods. Plot all four combinations in a mu-sigma diagram.

Next, use the power of `tsibble` to calculate rolling/growing versions of mu and sigma (e.g. start with 6 months of data). Try to plot the changing mu and sigma via an animation using `gganimate` (see [here](https://www.datanovia.com/en/blog/gganimate-how-to-create-plots-with-beautiful-animation-in-r/)).

```{r}
mult_stocks <- tq_get(c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD"),get = "stock.prices",from = "2000-01-01", to = "2020-09-24")
mult_Ra <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2000-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Mu")
mult_sigma <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2000-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Sigma")
```

```{r}
#In order to stack them to together makes a little bit easier.
mu_Ra <- aggregate(mult_Ra[3:3],list(mult_Ra$symbol),mean)
sigma_Ra <- aggregate(mult_sigma[3:3],list(mult_Ra$symbol),mean.stderr)
mult_musig <- left_join(mu_Ra, sigma_Ra, by = "Group.1")
```

```{r}
ggplot(mult_musig,aes(x=Sigma, y=Mu,label=Group.1)) + geom_point(alpha =0.6) + coord_fixed() + scale_x_log10() + scale_y_log10() + geom_text(aes(label=Group.1),hjust=0, vjust=0)
```

```{r}
ggplot(mult_musig,aes(x=Sigma, y=Mu)) + geom_point(alpha =0.6) + coord_fixed() + scale_x_log10() + scale_y_log10() + stat_smooth(method = "lm",col = "#C42126",se = FALSE, size=1)
```

```{r}
mult_period <- tq_get(c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD"),get = "stock.prices",from = "2005-01-01", to = "2020-09-24")
mult_Ra_period <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2005-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Mu")
mult_sigma_period <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2005-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Sigma")
```

```{r}
mu_Ra_period <- aggregate(mult_Ra_period[3:3],list(mult_Ra_period$symbol),mean)
sigma_Ra_period <- aggregate(mult_sigma_period[3:3],list(mult_Ra_period$symbol),mean.stderr)
mult_musig_period <- left_join(mu_Ra_period, sigma_Ra_period, by = "Group.1")
```

```{r}
ggplot(mult_musig_period,aes(x=Sigma, y=Mu, lable = Group.1)) + geom_point(alpha =0.6) + coord_fixed() + scale_x_log10() + scale_y_log10() + geom_text(aes(label=Group.1),hjust=0, vjust=0)
```

```{r}
mult_period_nd <- tq_get(c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD"),get = "stock.prices",from = "2010-01-01", to = "2020-09-24")
mult_Ra_period_nd <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2010-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Mu")
mult_sigma_period_nd <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2010-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Sigma")
```
```{r}
mu_Ra_period_nd <- aggregate(mult_Ra_period_nd[3:3],list(mult_Ra_period_nd$symbol),mean)
sigma_Ra_period_nd <- aggregate(mult_sigma_period_nd[3:3],list(mult_Ra_period_nd$symbol),mean.stderr)
mult_musig_period_nd <- left_join(mu_Ra_period_nd, sigma_Ra_period_nd, by = "Group.1")
```
```{r}
ggplot(mult_musig_period_nd,aes(x=Sigma, y=Mu, label=Group.1)) + geom_point(alpha =0.6) + coord_fixed() + scale_x_log10() + scale_y_log10() + geom_text(aes(label=Group.1),hjust=0, vjust=0)
```
```{r}
mult_period_rd <- tq_get(c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD"),get = "stock.prices",from = "2002-01-01", to = "2020-09-24")
mult_Ra_period_rd <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2002-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Mu")
mult_sigma_period_rd <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2002-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Sigma")

mu_Ra_period_rd <- aggregate(mult_Ra_period_rd[3:3],list(mult_Ra_period_rd$symbol),mean)
sigma_Ra_period_rd <- aggregate(mult_sigma_period_rd[3:3],list(mult_Ra_period_rd$symbol),mean.stderr)
mult_musig_period_rd <- left_join(mu_Ra_period_rd, sigma_Ra_period_rd, by = "Group.1")

ggplot(mult_musig_period_rd,aes(x=Sigma, y=Mu, label=Group.1)) + geom_point(alpha =0.6) + coord_fixed() + scale_x_log10() + scale_y_log10() + geom_text(aes(label=Group.1),hjust=0, vjust=0)
```
Stacking all plots in order to get the bigger picture.

```{r}
plot <- ggplot() + geom_point(data = mult_musig, aes(x=Sigma, y=Mu), color='green') + geom_point(data = mult_musig_period, aes(x=Sigma, y= Mu), color='red') + geom_point(data = mult_musig_period_nd ,aes(x = Sigma, y=Mu),color = 'blue') + geom_point(data= mult_musig_period_rd, aes(x=Sigma, y=Mu), color= 'orange')
plot
```
Next, use the power of Tsibble to calculate rolling/grwoing versions of mu and sigma (e.g. start with 6 months of data). Try to plot the changing mu and sigma via an animation using gganimate.

```{r}
pacman::p_load(gganimate,gifski,png,gapminder)
p <- ggplot(
gapminder,
aes(x = gdpPercap, y=lifeExp, size = pop, colour = country)
) +
geom_point(show.legend = FALSE, alpha = 0.7) +
scale_color_viridis_d() +
scale_size(range = c(2, 12)) +
scale_x_log10() +
labs(x = "GDP per capita", y = "Life expectancy")
p
p + transition_time(year) +
labs(title = "Year: {frame_time}")
```

```{r}
ov_mult_stocks <- tq_get(c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD"),get = "stock.prices",from = "2020-01-01", to = "2020-09-24")
ov_try_periode <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2020-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="daily",col_rename = "Return")
try_periode <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2020-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="daily",col_rename = "Sigma")
```
```{r}
mean_try <- aggregate(ov_try_periode[3:3],list(ov_try_periode$symbol),mean)
names(mean_try)[names(mean_try) == "Group.1"] <- "symbol"
ov_pp <- left_join(ov_try_periode, mean_try)

sigma_try <- aggregate(try_periode [3:3],list(try_periode$symbol), mean.stderr )
names(sigma_try)[names(sigma_try) == "Group.1"] <- "symbol"
ov_fin <- left_join(ov_pp, sigma_try)
```
```{r}
p <- ggplot(
ov_fin,
aes(x = Sigma, y= Return, size = Return, colour = symbol)
) +
geom_point(show.legend = FALSE, alpha = 0.7) +
scale_color_viridis_d() +
scale_size(range = c(2, 12)) +
scale_x_log10() +
labs(x = "Risk", y = "Return")
p
p + transition_time(date) +
labs(title = "date: {frame_time}")
```


## Exercise 3: Rolling regressions

Perform static and rolling regressions of four of your assets (monthly data, yearly window) on the S&P500 as well as the three Fama-French Factors (Mkt.RF, SMB and HML). Visualize the changing alphas and betas over time. You can use [this example](https://www.business-science.io/code-tools/2017/04/04/tidyquant-0-5-0.html), but I would prefer a use of the `tsibble`-package.



