---
title: "Portfoliomanagement and Financial Analysis - Assignment 2"
subtitle: "Submit until Monday 2020-09-28, 13:00"
author: "Amann, Matthias"
output: html_notebook
---


```{r load_packs}
pacman::p_load(tidyverse,tidyquant,FFdownload,tsibble)
```

**Please** remember to put your assignment solutions in `rmd` format using **many** chunks and putting readable text in between, similar to my examples given in Research Methods and Assignment 1! Also, each student has to select his own set of 10 stocks having data available as of `2000-01-01`. Select by Sharpe-ratio, dominance or any other method (e.g. matching your first name).


## Exercise 1: Performance Analysis of Portfolios

Create (using four of the ten stocks) multiple portfolios using `tq_portfolio()`:

*  an equally weighted one, 
*  a market-value weighted one, and 
*  one where you create a trading strategy according to [https://www.datacamp.com/community/tutorials/r-trading-tutorial](https://www.datacamp.com/community/tutorials/r-trading-tutorial) - use the tools in the tidyquant package!! Trade your four stocks in a way that Portfolios weights (in sum) do never exceed +-1.

DO a performance analysis a la `vignette("TQ05-performance-analysis-with-tidyquant")`.


```{r getting SP500 stocks}

#getting 10 stocks from sp500 index

AAPL <- tq_get("AAPL", get = "stock.prices", from =  "2000-01-01", to = "2019-09-17")
AMZN <- tq_get("AMZN", get = "stock-prices", from = "2000-01-01", to = "2019-09-17")
MSFT <- tq_get("MSFT", get = "stock.prices", from = "2000-01-01", to = "2019-09-17")
GOOG <- tq_get("MSFT", get = "stock.prices", from = "2000-01-01", to = "2019-09-17")
CSCO <- tq_get("CSCO", get = "stock.prices", from =  "2000-01-01", to = "2019-09-17")
QCOM <- tq_get("QCOM", get = "stock.prices", from =  "2000-01-01", to = "2019-09-17")
ADBE <- tq_get("ADBE", get = "stock.prices", from =  "2000-01-01", to = "2019-09-17")
NVDA <- tq_get("NVDA", get = "stock.prices", from =  "2000-01-01", to = "2019-09-17")
AMGN <- tq_get("AMGN", get = "stock.prices", from =  "2000-01-01", to = "2019-09-17")
GILD <- tq_get("GILD", get = "stock.prices", from =  "2000-01-01", to = "2019-09-17")

#select four stocks
#I choose CSCO, QCOM, NVDA, GILD because I like the companies
```

```{r Getting returns from the four stocks}
#we got all returns for the stocks in one tibble and renamed the column return 
monthly_returns_stocks <- c("CSCO", "QCOM", "NVDA", "GILD") %>%
  tq_get(get = "stock.prices", from = "2000-01-01", to = "2019-09-17") %>%
  group_by(symbol)%>%
  tq_transmute(adjusted, periodReturn, period = "monthly", col_rename =  "Ra")
monthly_returns_stocks
```
 
```{r Create baseline returns}
#to compare it with an index
monthly_returns_baseline <- "^GSPC" %>%
  tq_get(get = "stock.prices", from = "2000-01-01", to = "2019-09-17") %>%
  tq_transmute(adjusted, periodReturn, period = "monthly", col_rename = "Rb")
monthly_returns_baseline
```
```{r Aggregate portfolios}
#because we want 3 portfolios - we grow our portfolios, scalling a single portfolio to many
mult_monthly_returns_stocks <- monthly_returns_stocks %>%
  tq_repeat_df(n = 3)

mult_monthly_returns_stocks
```
```{r an equally weighted one}
#first portfolio is equally weight
#that is why we choose 25% for each

stock_returns_monthly <- c("CSCO", "QCOM", "NVDA","GILD") %>%
    tq_get(get  = "stock.prices",
           from = "2000-01-01",
           to   = "2019-09-17") %>%
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Ra")

#Second, get baseline asset returns, which is the exact same as Steps 1B and 2B from the Single Portfolio example.

baseline_returns_monthly <- "XLK" %>%
    tq_get(get  = "stock.prices",
           from = "2016-01-01",
           to   = "2019-12-31") %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Rb")

stock_returns_monthly_multi <- stock_returns_monthly %>%
    tq_repeat_df(n = 3)
stock_returns_monthly_multi


#Here’s what the weights table should look like for our example:

weights <- c(0.25, 0.25, 0.25, 0.25,
             0.25, 0.25, 0.25, 0.25,
             0.25, 0.25, 0.25, 0.25)

stocks <- c("CSCO", "QCOM", "NVDA","GILD")
weights_table <-  tibble(stocks) %>%
    tq_repeat_df(n = 3) %>%
    bind_cols(tibble(weights)) %>%
    group_by(portfolio)
weights_table

portfolio_returns_monthly_multi <- stock_returns_monthly_multi %>%
    tq_portfolio(assets_col  = symbol, 
                 returns_col = Ra, 
                 weights     = weights_table, 
                 col_rename  = "Ra")
portfolio_returns_monthly_multi



#Now just pass the expanded stock_returns_monthly_multi and the weights_table to tq_portfolio for portfolio aggregation.

portfolio_returns_monthly_multi <- mult_monthly_returns_stocks %>%
    tq_portfolio(assets_col  = symbol, 
                 returns_col = Ra, 
                 weights     = weights_table, 
                 col_rename  = "Ra")
portfolio_returns_monthly_multi
```



```{r a market-value weighted one}
library(rvest)
library(TTR)
#library(dygraphs)
library(lubridate)

#https://finance.yahoo.com/quote/QCOM?p=QCOM&.tsrc=fin-srch&guccounter=1
#marketcaps: CSCO=212.095B;GILD=83.434B;NVDA=109.748B;QCOM=94.87B
marketcaps <- c(212.095, 83.434, 109.748, 94.87)
#compute the weights
weights <- marketcaps /sum(marketcaps)
#inspect summary statistics
summary(weights)
#show the weights
weights
```
```{r market value weighted portfolio}
#CSCO = 42,41%
#GILD = 16,68%
#NVDA= 21,94%
#QCOM = 18,97%


#*  one where you create a trading strategy according to [https://www.datacamp.com/community/tutorials/r-trading-tutorial](https://www.datacamp.com/community/tutorials/r-trading-tutorial) - use the tools in the tidyquant package!! Trade your four stocks in a way that Portfolios weights (in sum) do never exceed +-1.
```

```{r finding out about our own trading strategy}
library(rvest)
library(TTR)
library(lubridate)

#sma is used to produce moving averages of the stock prices --> same weight for all historical data
#we produce moving averages because we need them for our "trend following" trading strategy to compare it

sma_CSCO <- SMA(CSCO[, "close"], n=50)
sma_GILD <- SMA(GILD[, "close"], n=50)
sma_NVDA <- SMA(NVDA[, "close"], n=50)
sma_QCOM <- SMA(QCOM[, "close"], n=50)

sma_CSCO_200 <- SMA(CSCO[, "close"], n=200)
sma_GILD_200 <- SMA(GILD[, "close"], n=200)
sma_NVDA_200 <- SMA(NVDA[, "close"], n=200)
sma_QCOM_200 <- SMA(QCOM[, "close"], n=200)

#alternatively you could have also used ema --> it gives more weight to current data --> maybe makes more sense
```
```{r creating dataframes for each stock with 200days and 50days moving averages}

library(tidyverse)
library(tidyquant)

#create a CSCO dataframe with the important data
CSCO_dates <- select(CSCO, date)
CSCO_dates

data.frame_CSCO <- data.frame(CSCO_dates, sma_CSCO_200, sma_CSCO)
data.frame_CSCO

#create a GILD dataframe with the important data
GILD_dates <- select(GILD, date)
GILD_dates

data.frame_GILD <- data.frame(GILD_dates, sma_GILD_200, sma_GILD)
data.frame_GILD

#create a QCOM dataframe with the important data
QCOM_dates <- select(QCOM, date)
QCOM_dates

data.frame_QCOM <- data.frame(QCOM_dates, sma_QCOM_200, sma_QCOM)
data.frame_QCOM

#creat a NVDA dataframe with the important data
NVDA_dates <- select(NVDA, date)
NVDA_dates

data.frame_NVDA <- data.frame(NVDA_dates, sma_NVDA_200, sma_NVDA)
data.frame_NVDA
```
```{r compare the second and the third colomn and fill them with 0 & 1}
# new column - fill with 0, but when 50day > 200 days, fill with 1

data.frame_CSCO['CSCO'] <- 0
data.frame_CSCO$CSCO[data.frame_CSCO$sma_CSCO > data.frame_CSCO$sma_CSCO_200] = 1  

data.frame_GILD['GILD'] <- 0
data.frame_GILD$GILD[data.frame_GILD$sma_GILD > data.frame_GILD$sma_GILD_200] = 1  

data.frame_QCOM['QCOM'] <- 0
data.frame_QCOM$QCOM[data.frame_QCOM$sma_QCOM > data.frame_QCOM$sma_QCOM_200] = 1  

data.frame_NVDA['NVDA'] <- 0
data.frame_NVDA$NVDA[data.frame_NVDA$sma_NVDA > data.frame_NVDA$sma_NVDA_200] = 1  
```
```{r sum up the colomn with 0 & 1}
#so we find out how many 1's are there --> on how many days we want to invest out of all
V_01 <- select(data.frame_CSCO, CSCO)
colSums(V_01, na.rm = TRUE)

nrow(data.frame_CSCO)
#calculate weight for CSCO
WEIGHT_CSCO <- colSums(V_01, na.rm = TRUE)/nrow(data.frame_CSCO)*100

V_02 <- select(data.frame_GILD, GILD)
colSums(V_02, na.rm = TRUE)

nrow(data.frame_GILD)
#calculate weight for GILD
WEIGHT_GILD <- colSums(V_02, na.rm = TRUE)/nrow(data.frame_GILD)*100

#calcuation for QCOM
V_03 <- select(data.frame_QCOM, QCOM)
colSums(V_03, na.rm = TRUE)

nrow(data.frame_QCOM)
#calculate weight QCOM
WEIGHT_QCOM <- colSums(V_03, na.rm = TRUE)/nrow(data.frame_QCOM)*100

#calculation for NVDA
V_04 <- select(data.frame_NVDA, NVDA)
colSums(V_04, na.rm = TRUE)

nrow(data.frame_NVDA)
#calculate weight NVDA
WEIGHT_NVDA <- colSums(V_04, na.rm = TRUE)/nrow(data.frame_NVDA)*100
```
```{r} 
#weight calculation 
all_weights <- sum(WEIGHT_CSCO, WEIGHT_GILD, WEIGHT_NVDA, WEIGHT_QCOM)

final_weight_CSCO <- WEIGHT_CSCO/all_weights
final_weight_GILD <- WEIGHT_GILD/all_weights
final_weight_NVDA <- WEIGHT_NVDA/all_weights
final_weight_QCOM <- WEIGHT_QCOM/all_weights


all_weights_tb <- tibble(final_weight_CSCO, final_weight_GILD, final_weight_QCOM, final_weight_NVDA)

rowSums(all_weights_tb)
```
```{r }
library(rvest)
library(TTR)
library(lubridate)
```

```{r create all the three portfolios}
#create new table of weights
weights_portfolio <- c(0.25, 0.25, 0.25, 0.25,
            weights[1], weights[2], weights[3], weights[4],
             final_weight_CSCO, final_weight_GILD, final_weight_QCOM, final_weight_NVDA)

stocks <- c("CSCO", "GILD", "NVDA", "QCOM")

weights_table <- tibble(stocks)%>%
    tq_repeat_df(n = 3) %>%
    bind_cols(tibble(weights_portfolio)) %>%
    group_by(portfolio)

weights_table
```
```{r we have to merge the expanded stock returns, the weights table for a portfolio aggregation}

portfolio_returns_monthly_multi <- mult_monthly_returns_stocks %>%
  tq_portfolio(assets_col = symbol,
               returns_col = Ra,
               weights = weights_table,
               col_rename = "Ra")
portfolio_returns_monthly_multi
```
```{r Merge with the baseline using date as the key}
multiple_portfolio <- left_join(portfolio_returns_monthly_multi,
                                monthly_returns_baseline,
                                by = "date")
multiple_portfolio
```


```{r performance calculation}
multiple_portfolio %>%
  tq_performance(Ra = Ra, Rb = Rb, performance_fun = table.CAPM)
```
```{r}
#Beta measures a security's sensitivity to market risk (the lower the better)
#alpha - difference from expected and required return (the higher the better)
```

```{r}
#Sharpe Ratio
multiple_portfolio %>%
  tq_performance(Ra = Ra, Rb = Rb, performance_fun = SharpeRatio)
#the higher the Sharpe Ratio the better
```






## Exercise 2: The mu/sigma diagram

For the 10 stocks in your sample, calculate mu and sigma for the entire and 3 subperiods. Plot all four combinations in a mu-sigma diagram.

Next, use the power of `tsibble` to calculate rolling/growing versions of mu and sigma (e.g. start with 6 months of data). Try to plot the changing mu and sigma via an animation using `gganimate` (see [here](https://www.datanovia.com/en/blog/gganimate-how-to-create-plots-with-beautiful-animation-in-r/)).


```{r Data Entire}
mult_stocks <- tq_get(c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD"),get = "stock.prices",from = "2000-01-01", to = "2020-09-24")
mult_Ra <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2000-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Mu")
mult_sigma <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2000-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Sigma")
```

```{r Mu/Sigma}
#In order to stack them to together makes a little bit easier.
mu_Ra <- aggregate(mult_Ra[3:3],list(mult_Ra$symbol),mean)
sigma_Ra <- aggregate(mult_sigma[3:3],list(mult_Ra$symbol),mean.stderr)
mult_musig <- left_join(mu_Ra, sigma_Ra, by = "Group.1")
```

```{r Plotting}
ggplot(mult_musig,aes(x=Sigma, y=Mu,label=Group.1)) + geom_point(alpha =0.6) + coord_fixed() + scale_x_log10() + scale_y_log10() + geom_text(aes(label=Group.1),hjust=0, vjust=0)
```
```{r}
ggplot(mult_musig,aes(x=Sigma, y=Mu)) + geom_point(alpha =0.6) + coord_fixed() + scale_x_log10() + scale_y_log10() + stat_smooth(method = "lm",col = "#C42126",se = FALSE, size=1)
```

```{r 1rst subperiod}
mult_period <- tq_get(c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD"),get = "stock.prices",from = "2005-01-01", to = "2020-09-24")
mult_Ra_period <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2005-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Mu")
mult_sigma_period <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2005-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Sigma")

mu_Ra_period <- aggregate(mult_Ra_period[3:3],list(mult_Ra_period$symbol),mean)
sigma_Ra_period <- aggregate(mult_sigma_period[3:3],list(mult_Ra_period$symbol),mean.stderr)
mult_musig_period <- left_join(mu_Ra_period, sigma_Ra_period, by = "Group.1")

ggplot(mult_musig_period,aes(x=Sigma, y=Mu, lable = Group.1)) + geom_point(alpha =0.6) + coord_fixed() + scale_x_log10() + scale_y_log10() + geom_text(aes(label=Group.1),hjust=0, vjust=0)
```

```{r 2nd subperiod}
mult_period_nd <- tq_get(c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD"),get = "stock.prices",from = "2010-01-01", to = "2020-09-24")
mult_Ra_period_nd <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2010-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Mu")
mult_sigma_period_nd <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2010-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Sigma")

mu_Ra_period_nd <- aggregate(mult_Ra_period_nd[3:3],list(mult_Ra_period_nd$symbol),mean)
sigma_Ra_period_nd <- aggregate(mult_sigma_period_nd[3:3],list(mult_Ra_period_nd$symbol),mean.stderr)
mult_musig_period_nd <- left_join(mu_Ra_period_nd, sigma_Ra_period_nd, by = "Group.1")

ggplot(mult_musig_period_nd,aes(x=Sigma, y=Mu, label=Group.1)) + geom_point(alpha =0.6) + coord_fixed() + scale_x_log10() + scale_y_log10() + geom_text(aes(label=Group.1),hjust=0, vjust=0)
```

```{r 3rd subperiod}
mult_period_rd <- tq_get(c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD"),get = "stock.prices",from = "2002-01-01", to = "2020-09-24")
mult_Ra_period_rd <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2002-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Mu")
mult_sigma_period_rd <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2002-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="yearly",col_rename = "Sigma")

mu_Ra_period_rd <- aggregate(mult_Ra_period_rd[3:3],list(mult_Ra_period_rd$symbol),mean)
sigma_Ra_period_rd <- aggregate(mult_sigma_period_rd[3:3],list(mult_Ra_period_rd$symbol),mean.stderr)
mult_musig_period_rd <- left_join(mu_Ra_period_rd, sigma_Ra_period_rd, by = "Group.1")

ggplot(mult_musig_period_rd,aes(x=Sigma, y=Mu, label=Group.1)) + geom_point(alpha =0.6) + coord_fixed() + scale_x_log10() + scale_y_log10() + geom_text(aes(label=Group.1),hjust=0, vjust=0)
```

Stacking all plots in order to get the bigger picture.

```{r Stacking all plots}
plot <- ggplot() + geom_point(data = mult_musig, aes(x=Sigma, y=Mu), color='green') + geom_point(data = mult_musig_period, aes(x=Sigma, y= Mu), color='red') + geom_point(data = mult_musig_period_nd ,aes(x = Sigma, y=Mu),color = 'blue') + geom_point(data= mult_musig_period_rd, aes(x=Sigma, y=Mu), color= 'orange')
plot
```


Next, use the power of `tsibble` to calculate rolling/growing versions of mu and sigma (e.g. start with 6 months of data). Try to plot the changing mu and sigma via an animation using `gganimate` (see [here](https://www.datanovia.com/en/blog/gganimate-how-to-create-plots-with-beautiful-animation-in-r/)).

```{r Example}
pacman::p_load(gganimate,gifski,png,gapminder)
p <- ggplot(
gapminder,
aes(x = gdpPercap, y=lifeExp, size = pop, colour = country)
) +
geom_point(show.legend = FALSE, alpha = 0.7) +
scale_color_viridis_d() +
scale_size(range = c(2, 12)) +
scale_x_log10() +
labs(x = "GDP per capita", y = "Life expectancy")
p
p + transition_time(year) +
labs(title = "Year: {frame_time}")
```

```{r Data}
ov_mult_stocks <- tq_get(c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD"),get = "stock.prices",from = "2020-01-01", to = "2020-09-24")
ov_try_periode <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2020-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="daily",col_rename = "Return")
try_periode <- c("AMZN","YUM","PG","JNJ","MSFT","AXP","BAC","FDX","F","HD") %>% tq_get(get= "stock.prices", from ="2020-01-01", to = "2020-09-24") %>% group_by(symbol) %>% tq_transmute(select = adjusted, mutate_fun = periodReturn, period ="daily",col_rename = "Sigma")
```

```{r Transfroming Data}
mean_try <- aggregate(ov_try_periode[3:3],list(ov_try_periode$symbol),mean)
names(mean_try)[names(mean_try) == "Group.1"] <- "symbol"
ov_pp <- left_join(ov_try_periode, mean_try)

sigma_try <- aggregate(try_periode [3:3],list(try_periode$symbol), mean.stderr )
names(sigma_try)[names(sigma_try) == "Group.1"] <- "symbol"
ov_fin <- left_join(ov_pp, sigma_try)
```

```{r animated dataset returns and sigma 2020}
p <- ggplot(
ov_fin,
aes(x = Sigma, y= Return, size = Return, colour = symbol)
) +
geom_point(show.legend = TRUE, alpha = 0.7) +
scale_color_viridis_d() +
scale_size(range = c(2, 12)) +
scale_x_log10() +
labs(x = "Risk", y = "Return")
p
p + transition_time(date) +
labs(title = "date: {frame_time}")
```







## Exercise 3: Rolling regressions

Perform static and rolling regressions of four of your assets (monthly data, yearly window) on the S&P500 as well as the three Fama-French Factors (Mkt.RF, SMB and HML). Visualize the changing alphas and betas over time. You can use [this example](https://www.business-science.io/code-tools/2017/04/04/tidyquant-0-5-0.html), but I would prefer a use of the `tsibble`-package.



```{r Exercise_3}
#### Rolling regressions ####
# a)
SP500_Stocks <- tq_index("S&P500")



# b) Download stock prices of stocks that had information at the 1.Jan.2000. 

SP500_2000<-c("MSFT", "QCOM", "AXP", "GILD") %>% tq_get(get  = "stock.prices",from = "2000-01-01", to   = "2019-12-31")


```


Download Farma-French

```{r}
tempf <- tempfile(fileext = ".RData"); tempd <- tempdir(); temptxt <- tempfile(fileext = ".txt")
inputlist <- c("F-F_Research_Data_Factors")
# Now process only these files if they can be matched (download only)
FFdownload(exclude_daily=TRUE,tempdir=tempd,download=TRUE,download_only=FALSE,inputlist=inputlist)
tempf2 <- tempfile(fileext = ".RData"); tempd2 <- tempdir() 
FFdownload(output_file = tempf2,tempdir = tempd2,exclude_daily = TRUE, download = TRUE, download_only=FALSE, listsave=temptxt)
load(tempf2)
ff<-FFdownload$x_Developed_3_Factors$monthly$Temp2
ff<-ff["2000/2019"]
sff<-timetk::tk_tbl(ff)
colnames(sff)[1]<-"date"
format(sff$date)
sff

```


#################### MONTHLY STOCK RETURNS ##########
```{r Exercise_3 Monthly Stock returns}
#### Monthly Stock returns for 4 Stocks ####
pacman::p_load(tidyverse,tidyquant,timetk)

sff <- filter(sff, date >= as.yearmon("Jan 2000"), date <= as.yearmon("Dec 2019"))

sff <- sff %>%
    select(date, Mkt.RF, RF)
sff

# Create a function to deliver the monthly returns since 2000-01-01
get_monthly_returns <- function(symbol){
  return <- tq_transmute(tq_get(symbol,
                                get = "stock.prices",
                                from = "2000-01-01",
                                to = "2019-12-31"),
                         select = adjusted,
                         col_rename = "monthly_return",
                         mutate_fun = periodReturn,
                         period = "monthly") %>%
    mutate(monthly_return = monthly_return * 100)
}

# Get the returns for four stocks
msft_return <- get_monthly_returns("MSFT")
msft_return %<>% mutate(date = zoo::as.yearmon(date))

qcom_return <- get_monthly_returns("QCOM")
qcom_return %<>% mutate(date = zoo::as.yearmon(date))

axp_return <- get_monthly_returns("AXP")
axp_return %<>% mutate(date = zoo::as.yearmon(date))

gild_return <- get_monthly_returns("GILD")
gild_return %<>% mutate(date = zoo::as.yearmon(date))

#merge the two datasets (stock return & sff)
joined_data_msft <- merge(msft_return, sff, by="date")
joined_data_msft

joined_data_qcom <- merge(qcom_return, sff, by ="date")
joined_data_qcom

joined_data_axp <- merge(axp_return, sff, by = "date")
joined_data_axp 

joined_data_gild <- merge(gild_return, sff, by = "date")
joined_data_gild
```
market risk free rate and risk free rate

################ RETURNS MINUS RISK FREE RATE #################
```{r Exercise_3 Set risk factors}
#### Combine monthly Stock returns and risk factors ####
#Remembering that the left side of the CAPM formula is CSCO return minus the risk free rate, we calculate that as well

joined_data_msft <- mutate(joined_data_msft, monthly_ret_RF = monthly_return - RF)
joined_data_qcom <- mutate(joined_data_qcom, monthly_ret_RF = monthly_return - RF)
joined_data_axp <- mutate(joined_data_axp, monthly_ret_RF = monthly_return - RF)
joined_data_gild <- mutate(joined_data_gild, monthly_ret_RF = monthly_return - RF)
```

---------------------------------------------------------------

######## Rolling CAPM OF 4 STOCKS ####################
```{r Exercise_3 Add the Rolling CAPM}
####  Add the Rolling CAPM to the Tibble for each Stock ####
require(zoo)
#rolling CAPM CSCO

add_rolling_capm <- function(joined_data_symbol){
  regr_fun <- function(data_xts) {
    lm(monthly_ret_RF ~ Mkt.RF, data = as_tibble(data_xts)) %>% coef()
  }
  
  return <- joined_data_symbol %>%
    tq_mutate(mutate_fun = rollapply,
              width = 60, # 60 data (tibble) rows // 60 rows / 12 months = 5 years
              FUN = regr_fun,
              by.column = FALSE,
              col_rename = c("alpha", "beta"))
}

joined_data_msft <- add_rolling_capm(joined_data_msft)
joined_data_qcom <- add_rolling_capm(joined_data_qcom)
joined_data_axp <- add_rolling_capm(joined_data_axp)
joined_data_gild <- add_rolling_capm(joined_data_gild)
```

######## PLOTTING ALPHA ####################
```{r Exercise_3 Plot alpha}

#### plot alpha ####
create_alpha_plot <- function(joined_data_symbol, title) {
  filter(joined_data_symbol, !is.na(alpha)) %>%
    ggplot(aes(x = date, y = alpha)) + 
        geom_line(size = 1, color = palette_light()[[1]]) + 
        geom_smooth() +
        labs(title = title, x = "") +
        theme_tq(base_size = 18)
}

create_alpha_plot(joined_data_msft, "Microsoft: 5 year rolling CAPM - alpha")
create_alpha_plot(joined_data_qcom, "Qualcomm: 5 year rolling CAPM - alpha")
create_alpha_plot(joined_data_axp, "American Express: 5 year rolling CAPM - alpha")
create_alpha_plot(joined_data_gild, "Gilead Sciences: 5 year rolling CAPM - alpha")
```
Alpha is the performances of the investors compared to the market in %

######## PLOTTING BETA#####
```{r Exercise_3 Plot beta}

#### plot beta ####
create_beta_plot <- function(joined_data_symbol, title) {
  filter(joined_data_symbol, !is.na(alpha)) %>%
  ggplot(aes(x = date, y = beta))  + 
      geom_rect(xmin = as.yearmon("Jan 2008"), 
                xmax = as.yearmon("Mar 2009"), 
                ymin = 0, ymax = 10.0, 
                fill = palette_light()[[4]], alpha = 0.01) + 
      geom_line(size = 1, color = palette_light()[[1]]) +
      labs(title = title, x = "") + 
      theme_tq(base_size = 18)
}

create_beta_plot(joined_data_msft, "Microsoft: 5 year rolling CAPM - beta")
create_beta_plot(joined_data_qcom, "Qualcomm: 5 year rolling CAPM - beta")
create_beta_plot(joined_data_axp, "American Express: 5 year rolling CAPM - beta")
create_beta_plot(joined_data_gild, "Gilead Sciences: 5 year rolling CAPM - beta")
```
Beta is the volatiliti of the market. Between 0 (low) and 2 (extremely volatile). 

######## PLOTTING ALL ####################
```{r Exercise_3 Plot all}

#### Ploting all four CAPM alpha ####
# union two dataframes without duplicates 

joined_data <- rbind(
  add_column(select(joined_data_msft, alpha, beta, date), "symbol" = "MSFT"),
  add_column(select(joined_data_gild, alpha, beta, date), "symbol" = "GILD"),
  add_column(select(joined_data_axp, alpha, beta, date), "symbol" = "AXP"),
  add_column(select(joined_data_qcom, alpha, beta, date), "symbol" = "QCOM")
)
joined_data <- filter(joined_data, date >= as.yearmon("Jan 2005"))

joined_data %>%
    ggplot(aes(x = date, y = alpha)) +
    geom_line(size = 1, color = palette_light()[[1]]) + 
    geom_smooth() +
    labs(title = "Stocks: 5 year rolling CAPM - alpha", x = "",
         subtitle = "Rolling alpha is steadily trending upwards") +
    facet_wrap(~ symbol, ncol = 2) +
    theme_tq()
```


```{r}
#### Ploting all four CAPM beta ####
joined_data %>%
ggplot(aes(x = date, y = beta))  + 
    geom_rect(xmin = as.yearmon("Jan 2008"), 
              xmax = as.yearmon("Mar 2009"), 
              ymin = 0, ymax = 10.0, 
              fill = palette_light()[[4]], alpha = 0.01) + 
    geom_line(size = 1, color = palette_light()[[1]]) +
    labs(title = "Stocks: 5 year rolling CAPM - beta", x = "") +
    facet_wrap(~ symbol, ncol = 2) +
    theme_tq()
```



